On the uniqueness and stability of dictionaries \\ for sparse representation of noisy signals

### 2019-07-22 manuscripts/IEEE/final_submission_final.tex
Updates from Overleaf

\begin{figure}
\begin{center}
\includegraphics[width=.24 \linewidth]{figs/basis.png}
% \includegraphics[width=.25 \linewidth]{figs/Ahat_FastICA_M640_K8_noise0_2042}
%\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise0_4083.png}
\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M1280_K8_2.png}
\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M1280_K8_3.png}
\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M1280_K8_4.png}
\caption{\textbf{Learning a dictionary from increasingly noisy data}. The (unraveled) basis elements of the $8 \times 8$ discrete cosine transform (DCT) form the 64 columns of the left-most matrix above. Three increasingly imprecise dictionaries (columns reordered to best match original) are recovered by FastICA \cite{hyvarinen2000independent} trained on data generated from $8$-sparse linear combinations of DCT elements corrupted with additive noise (increasing from left to right).}
\vspace{-.6 cm}
\label{noisyrecovery}
\end{center}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=.24 \linewidth]{manuscripts/IEEE/figs/Basis_.png}
% \includegraphics[width=.25 \linewidth]{figs/Ahat_FastICA_M640_K8_noise0_2042}
%\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise0_4083.png}
\includegraphics[width=.24 \linewidth]{manuscripts/IEEE/figs/Ahat_FastICA_M1280_K8_noise0_0001.png}
\includegraphics[width=.24 \linewidth]{manuscripts/IEEE/figs/Ahat_FastICA_M1280_K8_noise2_0513.png}
\includegraphics[width=.24 \linewidth]{manuscripts/IEEE/figs/Ahat_FastICA_M1280_K8_noise3_9744.png}
\caption{\textbf{Learning a dictionary from increasingly noisy data}. The (unraveled) basis elements of the $8 \times 8$ discrete cosine transform (DCT) form the 64 columns of the left-most matrix above. Three increasingly imprecise dictionaries (columns reordered to best match original) are recovered by FastICA \cite{hyvarinen2000independent} trained on data generated from $8$-sparse linear combinations of DCT elements corrupted with additive noise (increasing from left to right).}
\vspace{-.6 cm}
\label{noisyrecovery}
\end{center}
\end{figure}
